D3064R0: Bringing the Laws of Physics, Computer-System Constraints, and Compilers to Bear on the OOTA Problem

### 2024-02-14 ootavacuous.tex
Add transition paragraph to "C++ Compilers" section
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>
Back-reference atomic-load invention
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

@@

This section contains several example litmus tests from the active
mind of Alan Stern.

>>>>

Given this relation between abstract and hardware executions, it is time
to turn our attention to the tool that selects hardware execution so as
to preserve that relation, namely, compilers.

@@

This section contains several example litmus tests from the active
mind of Alan Stern, expanding on the material presented in
Section~\ref{sec:Inventing Atomic Loads Can Destroy Semantic Dependencies}.
